---
title: "Additional figures for RNA-seq analysis"
output: html_document
---


Venn diagram
======================
Venn (upreg Wt/Tbud/InjCap) (attached table of GO terms for overlaps) 
	- Where no significant GO terms, use top term as a ‘descriptor’. 
Venn (upreg Nr/Pnt/ConCap) (attached table of GO terms for overlaps)

Data
```{r}
load("~/Documents/tuxedoRNASeq/geneAnalysis/DESeq2/rld2.RData")
# Which auto-loads DESeq2

load("~/Documents/tuxedoRNASeq/geneAnalysis/DESeq2/DESeq2_negRegGenes.RData")
load("~/Documents/tuxedoRNASeq/geneAnalysis/DESeq2/DESeq2_posRegGenes.RData")

rld_negGenes <- lapply(1:length(DESeq2_negRegGenes),function(x) assay(rld2)[which(rownames(assay(rld2)) %in%DESeq2_negRegGenes[[x]]),])
rld_negGenes <- lapply(1:3,function(x) rld_negGenes[[x]] - rowMeans(rld_negGenes[[x]]))

rld_posGenes <- lapply(1:length(DESeq2_posRegGenes),function(x) assay(rld2)[which(rownames(assay(rld2)) %in%DESeq2_posRegGenes[[x]]),])
rld_posGenes <- lapply(1:3,function(x) rld_posGenes[[x]] - rowMeans(rld_posGenes[[x]]))

names(rld_negGenes) <- c("UpregulatedInNR","UpregulatedInPNT","UpregulatedInInjCap")
names(rld_posGenes) <- c("UpregulatedInWT","UpregulatedInTbud","UpregulatedInConCap")

names(rld_posGenes)
names(rld_negGenes)
```


Use the vennDiagram package to draw plots

```{r}
source("https://bioconductor.org/biocLite.R")
biocLite()
biocLite("VennDiagram")
library("VennDiagram")

load("~/Documents/tuxedoRNASeq/geneAnalysis/DESeq2/rld2.RData")
# Which auto-loads DESeq2

load("~/Documents/tuxedoRNASeq/geneAnalysis/DESeq2/DESeq2_negRegGenes.RData")
load("~/Documents/tuxedoRNASeq/geneAnalysis/DESeq2/DESeq2_posRegGenes.RData")

rld_negGenes <- lapply(1:length(DESeq2_negRegGenes),function(x) assay(rld2)[which(rownames(assay(rld2)) %in%DESeq2_negRegGenes[[x]]),])
rld_negGenes <- lapply(1:3,function(x) rld_negGenes[[x]] - rowMeans(rld_negGenes[[x]]))

rld_posGenes <- lapply(1:length(DESeq2_posRegGenes),function(x) assay(rld2)[which(rownames(assay(rld2)) %in%DESeq2_posRegGenes[[x]]),])
rld_posGenes <- lapply(1:3,function(x) rld_posGenes[[x]] - rowMeans(rld_posGenes[[x]]))

names(rld_negGenes) <- c("UpregulatedInNR","UpregulatedInPNT","UpregulatedInInjCap")
names(rld_posGenes) <- c("UpregulatedInWT","UpregulatedInTbud","UpregulatedInConCap")

names(rld_posGenes)

venn.diagram(
x = list(rownames(rld_posGenes[[1]]),rownames(rld_posGenes[[2]]),rownames(rld_negGenes[[3]])),
category.names = c("Wildtype" , "Tbud" , "InjCap"),
filename = '~/Documents/tuxedoRNASeq/geneAnalysis/DESeq2/Venn_UpregulatedIn_wtTbudInjCap',
        output = TRUE ,
        imagetype="png" ,
        height = 680 , 
        width = 680 , 
        resolution = 300,
        compression = "lzw",
        lwd = 5,
        lty = 'blank', 
        fill = c('cornflowerblue', 'yellow', 'darkorchid1'),
        cex = 1,
        fontface = "bold",
        fontfamily = "sans",
        cat.cex = 0.5,
        cat.fontface = "bold",
        cat.default.pos = "outer",
        cat.pos = c(-27, 27, 135),
        cat.dist = c(0.055, 0.055, 0.085),
        cat.fontfamily = "sans",
        rotation = 1
        )

venn.diagram(
x = list(rownames(rld_negGenes[[1]]),rownames(rld_negGenes[[2]]),rownames(rld_posGenes[[3]])),
category.names = c("Nr" , "PNT" , "ConCap"),
filename = '~/Documents/tuxedoRNASeq/geneAnalysis/DESeq2/Venn_UpregulatedIn_nrPntConCap',
        output = TRUE ,
        imagetype="png" ,
        height = 680 , 
        width = 680 , 
        resolution = 300,
        compression = "lzw",
        lwd = 5,
        lty = 'blank', 
        fill = c('cornflowerblue', 'yellow', 'darkorchid1'),
        cex = 1,
        fontface = "bold",
        fontfamily = "sans",
        cat.cex = 0.5,
        cat.fontface = "bold",
        cat.default.pos = "outer",
        cat.pos = c(-27, 27, 135),
        cat.dist = c(0.055, 0.055, 0.085),
        cat.fontfamily = "sans",
        rotation = 1
        )

```


The venn diagrams show that there are 362 genes upregulated in both InjCap and Tbud, and 102 upregulated in both InjCap/WT, and 27 between Tbud/Wt. 
There are also equivalents for the Nr/PNT/ConCap groups.
Pull out and save these gene lists.
Create heatmaps for these overlaps.
```{r}
library(limma)
table(rownames(rld_posGenes[[1]]) %in% rownames(rld_posGenes[[2]])) # 27 genes overlap
overlap_WtTbud <- unique(strsplit2(rownames(rld_posGenes[[1]])[rownames(rld_posGenes[[1]]) %in% rownames(rld_posGenes[[2]])],".",fixed=T)[,1])
overlap_WtInjCap <- unique(strsplit2(rownames(rld_posGenes[[1]])[rownames(rld_posGenes[[1]]) %in% rownames(rld_negGenes[[3]])],".",fixed=T)[,1])
overlap_TbudInjCap <- unique(strsplit2(rownames(rld_posGenes[[2]])[rownames(rld_posGenes[[2]]) %in% rownames(rld_negGenes[[3]])],".",fixed=T)[,1])
overlap_TbudInj_rmLOC <- overlap_TbudInjCap[-grep("LOC",overlap_TbudInjCap)]

overlap_NrPNT <- unique(strsplit2(rownames(rld_negGenes[[1]])[rownames(rld_negGenes[[1]]) %in% rownames(rld_negGenes[[2]])],".",fixed=T)[,1])
overlap_NrConCap <- unique(strsplit2(rownames(rld_negGenes[[1]])[rownames(rld_negGenes[[1]]) %in% rownames(rld_posGenes[[3]])],".",fixed=T)[,1])
overlap_PntConCap <- unique(strsplit2(rownames(rld_negGenes[[2]])[rownames(rld_negGenes[[2]]) %in% rownames(rld_posGenes[[3]])],".",fixed=T)[,1])
overlap_PntCon_rmLOC <- overlap_PntConCap[-grep("LOC",overlap_PntConCap)]

# Save these gene names for use in PANTHER
# write.table(overlap_WtTbud,file='~/Documents/tuxedoRNASeq/geneAnalysis/DESeq2/refseqGeneNames/overlap_WtTbud.csv',sep="\t",row.names=F, col.names=F) Doesn't work with PANTHER for some reason
write.csv(overlap_WtTbud,file='~/Documents/tuxedoRNASeq/geneAnalysis/DESeq2/refseqGeneNames/overlap_WtTbud.csv')
write.csv(overlap_WtInjCap,file='~/Documents/tuxedoRNASeq/geneAnalysis/DESeq2/refseqGeneNames/overlap_WtInjCap.csv')
write.csv(overlap_TbudInjCap,file='~/Documents/tuxedoRNASeq/geneAnalysis/DESeq2/refseqGeneNames/overlap_TbudInjCap.csv')
write.csv(overlap_TbudInj_rmLOC,file='~/Documents/tuxedoRNASeq/geneAnalysis/DESeq2/refseqGeneNames/overlap_TbudInj_rmLOC.csv')

write.csv(overlap_NrPNT,file='~/Documents/tuxedoRNASeq/geneAnalysis/DESeq2/refseqGeneNames/overlap_NrPNT.csv')
write.csv(overlap_NrConCap,file='~/Documents/tuxedoRNASeq/geneAnalysis/DESeq2/refseqGeneNames/overlap_NrConCap.csv')
write.csv(overlap_PntConCap,file='~/Documents/tuxedoRNASeq/geneAnalysis/DESeq2/refseqGeneNames/overlap_PntConCap.csv')
write.csv(overlap_PntCon_rmLOC,file='~/Documents/tuxedoRNASeq/geneAnalysis/DESeq2/refseqGeneNames/overlap_PntCon_rmLOC.csv')
```







